D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-22 ootavacuous.tex
Move oota-invent-int-load.litmus to D.6
Also fix up dead cross-reference while in the area.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Most of the examples in this paper involve simple semantic dependencies
connecting a single load to a single store.
One exception appears in
Appendix~\ref{app:Non-LB Litmus Test},
but this section will present a more difficult example.

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-invent-int-load.litmus @@
\caption{Inventing Non-Boolean Atomic Loads}
\label{lst:Unused Inventing Non-Boolean Atomic Loads}
\end{listing}

This issue is not restricted to booleans.
For example, if given the code fragment shown in
Figure~\ref{lst:OOTA Cycle}
on
page~\pageref{lst:OOTA Cycle},
is the compiler permitted to act as if the code was instead as shown in
Listing~\ref{lst:Unused Inventing Non-Boolean Atomic Loads}?
Here, if the value loaded by line~9 is something other than 42,
the load is retried on line~11, and perhaps a third time on line~14.
If the value loaded in all three cases is something other than 42,
then line~16 stores the last value loaded, and otherwise, the constant
42 is stored by either line~18, 20, or~23.
Despite the fact that the code in both listings can be argued to be
equivalent, it is difficult to imagine that a reasonable compiler
would act as if the code in
Figure~\ref{lst:OOTA Cycle}
was instead that shown in
Listing~\ref{lst:Unused Inventing Non-Boolean Atomic Loads}.

@@

This section lists a couple of other litmus tests of interest:

\begin{itemize}
\item	The litmus test at
	\url{https://github.com/paulmckrcu/oota/blob/master/litmus/oota-two-source.litmus}
	shows multiple overlapping OOTA cycles.
\item	The litmus test at
	\url{https://github.com/paulmckrcu/oota/blob/master/litmus/oota-non-lb.litmus}
	shows that OOTA cycles are not confined to the load-buffering (LB)
	pattern.
\end{itemize}

>>>>

Most of the examples in this paper involve simple semantic dependencies
connecting a single load to a single store.
One exception appears in
Appendix~\ref{app:Additional Litmus Tests},
but this section will present a more difficult example.

@@

@@

This section lists a few other litmus tests of interest:

\begin{itemize}
\item	The litmus test at
	\url{https://github.com/paulmckrcu/oota/blob/master/litmus/oota-two-source.litmus}
	shows multiple overlapping OOTA cycles.
\item	The litmus test at
	\url{https://github.com/paulmckrcu/oota/blob/master/litmus/oota-non-lb.litmus}
	shows that OOTA cycles are not confined to the load-buffering (LB)
	pattern.
\item	The litmus test at
	\url{https://github.com/paulmckrcu/oota/blob/master/litmus/oota-invent-int-load.litmus}
	shows another invented-load scenario loosely based on
	Figure~\ref{lst:OOTA Cycle}
	on
	page~\pageref{lst:OOTA Cycle}.
	See Appendix~\ref{app:Inventing Atomic Loads}
	for more discussion on this topic.
\end{itemize}
